% --- resumo em inglês ---

\begin{OnehalfSpacing} 

\noindent \imprimirAutorCitacaoMaiuscula. {\bfseries\imprimirtitulo}. {\imprimirdata}.  Monografia -- Curso de {\MakeUppercase\imprimircurso}, {\imprimirinstituicao}, {\imprimirlocal}, {\imprimirdata}.

\vspace{\onelineskip}
\vspace{\onelineskip}
\vspace{\onelineskip}
\vspace{\onelineskip}

\begin{resumo}[Abstract]%
\begin{otherlanguage*}{english}%
\textit{
%início do texto do abstract
\noindent This research presents the study about graph databases applied to search for temporary workmanship by using the same business model adopted by social networks. This is an applied research, since it aims to propose a solution for a real social problem that happens inside a specific region but it can be helpful to the entire population. It was used the graph database Neo4j, together with the API Cypher to navigate and also to data management on database. This research also covers the creation of a web based software which was created using the front-end technologies HTML, CSS, Javascript and the framework Angular JS, in client side and, it was used Java programming language, on server-side, to create a REST Web service which work together with Neo4j and provide information on client side. In order to benefit the service providers as well as contractors, some functionalities have been developed to help them in decision-making. As example, it is possible to quote the search for a particular type of service, performance analysis of the professionals, creation of partners network. The application also have comparative graphs which display information about the last evaluations to the users. These functionalities have brought a high relevance to social, technical and theoretical areas because it explored new resources related to NoSQL databases. So, it is possible to conclude that the objectives proposed by this work were met.
%fim do texto do abstract
}

\vspace{\onelineskip}
\vspace*{\fill}
\noindent \textbf{Keywords}: \imprimirKeyWordOne. \imprimirKeyWordTwo. \imprimirKeyWordThree.
\end{otherlanguage*}
\vspace{\onelineskip}
\end{resumo}

\end{OnehalfSpacing}
